MCMC convergence diagnostics

### 2023-07-18 src/naomi-simple_mcmc/mcmc-convergence.Rmd
Add check of BYM2 correlation between standard deviation and proprotion, and save AR1 and BYM2 results for inclusion in manuscript

```{r}
bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_alpha_as", "logit_phi_alpha_as"), diag_fun = "hist", off_diag_fun = "hex")
bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_rho_as", "logit_phi_rho_as"), diag_fun = "hist", off_diag_fun = "hex")
bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_alpha_a", "logit_phi_alpha_a"), diag_fun = "hist", off_diag_fun = "hex")
(plot <- bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_rho_a", "logit_phi_rho_a"), diag_fun = "hist", off_diag_fun = "hex"))

ggsave("rho_a.png", plot, h = 4, w = 6.25)
```

>>>>

```{r}
bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_alpha_a", "logit_phi_alpha_a"), diag_fun = "hist", off_diag_fun = "hex")
bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_alpha_as", "logit_phi_alpha_as"), diag_fun = "hist", off_diag_fun = "hex")
bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_rho_as", "logit_phi_rho_as"), diag_fun = "hist", off_diag_fun = "hex")
bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_rho_a", "logit_phi_rho_a"), diag_fun = "hist", off_diag_fun = "hex")

ggsave("rho_a.png", h = 4, w = 6.25)

get_correlation <- function(par) {
  cor(as.data.frame(rstan::extract(mcmc, c(paste0("log_sigma_", par), paste0("logit_phi_", par)))))[1, 2]
}

ar1_cor_df <- data.frame(
  par = c("alpha_a", "alpha_as", "rho_as", "rho_a"),
  type = "ar1"
) %>%
  mutate(cor = purrr::map_dbl(get_correlation, .x = par))

ar1_cor_df
```

## BYM2 orthogonality

Does the supposed orthogonality of the BYM2 model play out?
Looks like the answer is mostly yes.

```{r}
bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_rho_x", "logit_phi_rho_x"), diag_fun = "hist", off_diag_fun = "hex")
bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_rho_xs", "logit_phi_rho_xs"), diag_fun = "hist", off_diag_fun = "hex")
bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_alpha_xs", "logit_phi_alpha_xs"), diag_fun = "hist", off_diag_fun = "hex")
bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_alpha_x", "logit_phi_alpha_x"), diag_fun = "hist", off_diag_fun = "hex")

ggsave("alpha_x.png", h = 4, w = 6.25)

bym2_cor_df <- data.frame(
  par = c("rho_x", "rho_xs", "alpha_x", "alpha_xs"),
  type = "bym2"
) %>%
  mutate(cor = purrr::map_dbl(get_correlation, .x = par))

bym2_cor_df

write_csv(bind_rows(ar1_cor_df, bym2_cor_df), file = "ar1-bym2-cor.csv")
```
